---
title: "Batch Reduce Stable Sr - Template"
output: html_document
editor_options: 
  chunk_output_type: console
---

This script is for batch reducing spike Sr data to get delta 88/86Sr and fractionation corrected 87Sr/86Sr

For this to work correctly it's very important that the input raw data tables are formatted as described below; the batch.reduce function differentiates samples using indexing not column names.

--- Necessary Packages + Functions ---
```{r}
library(tidyverse)
library(ggthemes)
library(googlesheets4)
source("reduce_functions.R")
```


--- Spike Composition ---
```{r}
spike_comp <- tibble(
  sp_86_84 = 0.051524,
  sp_87_84 = 0.787050,
  sp_88_84 = 0.218766,
)
```


--- Import + Organize Data ---

The final result of this section should be:
(1) a data-frame of raw spiked data with n_samples*3 columns, organized such that col1 = sample_1 86/84, col2 = sample_1 88/84, col3 = sample_1 87/84, col4 = sample_2 86/84,
    col5 = sample_2 88/84, ... col(n_samples*3) = sample_n 87/84
(2) a tibble of unspiked data that has n_samples rows, and two columns, the first being a sample name and the second the mean unspiked 87/86 ratios
(3) a double of how many samples you're trying to reduce


Import from google sheets -- assumes everything is already in the correct format
```{r}
### Spiked Data ###
spiked_data <- read_sheet("")

### Unspiked Data ###
unspiked_data <- read_sheet("")

### Declare number of samples ### 
n_samples = 
```


--- Batch Reduce ----
```{r}
reduced_data <- batch.reduce(n_samples = n_samples, id_data = spiked_data, ic_data = unspiked_data, spike_comp = spike_comp)
```



--- Reduce One Sample (troubleshooting) ---
```{r}

exp_data <- read_sheet("")

id_86_84 <- exp_data$id_86_84
id_87_84 <- exp_data$id_87_84
id_88_84 <- exp_data$id_88_84
ic_87_86 <- 0.70916581

exp <- get.stable(id_86_84, id_87_84, id_88_84, ic_87_86, spike_comp)
```





